Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-09-23 manuscript/supplemental_material.Rnw
load common placenta classification table

<<placental_classification,echo=FALSE,results="hide",cache.extra=file.info(dir("../data","placenta.*classification.*",full.names=TRUE))[,"mtime"]>>=
placenta_classification <- fread("../data/placental_classification.txt")
load("../data/placenta_classification_p")
for (mf.bp in c("mf","bp")) {
    for (class in c("interdigitation","barrier","shape")) {
        load(paste0("../data/placenta_classification_go_",mf.bp,"_",class))
    }
}

@@

\begin{table}[hb]
<<placental_classification_table,echo=FALSE,results="asis">>=
print(xtable(placental.classification,
             display=c("s","s","s","s","s"),
             align=c("c","c","c","c","c")),
      include.rownames=FALSE,
      floating=FALSE,
      booktabs=TRUE
      )

>>>>

<<placental_classification,echo=FALSE,results="hide",cache.extra=file.info(dir("../data","placenta.*classification.*",full.names=TRUE))[,"mtime"]>>=
load("../data/placenta_classification")
load("../data/placenta_classification_p")
for (mf.bp in c("mf","bp")) {
    for (class in c("interdigitation","barrier","shape")) {
        load(paste0("../data/placenta_classification_go_",mf.bp,"_",class))
    }
}

@@

\begin{table}[hb]
<<placental_classification_table,echo=FALSE,results="asis">>=
print(xtable(placenta_classification,
             display=c("s","s","s","s","s"),
             align=c("c","c","c","c","c")),
      include.rownames=FALSE,
      floating=FALSE,
      booktabs=TRUE
      )
